Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER.

>>>>

We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER. 
This suggests that our model has better speech quality compared with discriminative models but 
worse in speech intelligibility. One possible reason might be related 
to the discretization process on the mixture 
speech. Our Kmeans algorithm is trained on clean speech instead of mixed speech. 
Discretization on the mixed
speech might cause the output to focus on wrong speakers. Our results from TSELM-L-Hybrid proves this. For TSELM-L-Hybrid, we use the continuous 
embeddings from mixture speech and it has
